Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
What happens if edge server is inside censor's network.

% Edge servers within the censored region.
% Censor could block on the way to the origin server,
% if the censor has visibility to it.
% Maybe the CDN has its own private high-speed cables,
% or it VPNs its own stuff or something.

>>>>

We have assumed that the intermediate web service is
outside the censor's domain of control,
so that communication between the web service and Tor bridge
doesn't have to be protected.
What happens when the web service---a CDN edge server, for instance---is
inside the network controlled by the censor?
If the edge server forwards the request to the Tor bridge
as an ordinary HTTP request on the public Internet,
then blocking it is as easy as blocking the IP address of the bridge.
On the other hand, if the web service encapsulates
the request and sends it encrypted, or over its own fast private network,
to another server outside of the censor's control,
then fronting will still work.
